Mathematical Aspects of the Capital Market

### 2017-08-04 phd/Chapterintroduction.tex
Some minor arrangements.

Kesten \cite{kesten:1973} showed that, when $A_t$ and $B_t$ were almost
surely non-negative, had no row or column of only zeros, and there was
a positive probability that $B_t$ was strictly positive, the strictly
stationary solution to the equation
$V \overset{d}{=} A V + B$ had power-law tails
for its marginal distributions, assuming the following conditions (M)
and (A):
\begin{itemize}
\item Condition (M)
  \begin{enumerate}
  \item The top Lyapunov exponent
    \[
    \gamma = \inf_{n \geq 1} {1 \over n}\E \log \|A_n \cdots A_1\|
    \]
    is negative.
  \item There exists $\xi > 0$ such that
    \[
    1 = \lambda(\xi) = \lim_{n \to \infty} {1 \over n} \log \E \|A_n \cdots A_1\|^\xi
    \]
  \item $\E (\|A_1\|^\xi \log^+\|A_1\|) < \infty$
  \item $\E |B_1|^\xi < \infty$
  \end{enumerate}
\item Condition (A) : The group generated by
  \[
  \{\log\rho(s): s = A_n \cdots A_1 \text{ for some } n \geq 1\}
  \]
  is dense in $\reals$, where $\rho(s)$ denotes the spectral
  radius of matrix $s$.
\end{itemize}
Upon these conditions, Kesten's theorem gives
\begin{equation*}
  u^\xi \P(u^{-1} V \in \cdot) \overset{v}{\to} \mu_\xi(\cdot)
\end{equation*}
where $\mu_\xi$ is a non-null Radon measure on
$\reals^d_+ \setminus \{0\}$ with the property
$\mu_\xi(a A) = a^{-\xi} \mu_\xi(A)$.

Recently, Collamore and Mentemeier \cite{collamore:mentemeier:2016}
extended Kesten's result and gave an explicit expression for $\mu_\xi$:
\begin{equation}
  \label{eq:CollamoreMentemeierIntro}
  \lim_{u \to \infty} u^{\xi} \E \left[
    f(u^{-1} V)
    \right]
  =
  {C \over \lambda'(\xi)}  
  \int_{\sphere^{d-1}_+ \times R} e^{-\xi s} f(e^s x) \ell_\xi(dx) ds
\end{equation}
where $C$ is a constant (cf. eq.(2.15) of Collamore and Mentemeier
\cite{collamore:mentemeier:2016}), $f(\cdot)$ is any bounded
continuous function on $\reals^{d}_+ \setminus \{0\}$  and
$\ell_\xi$ is a probability measure on $\sphere_+^{d-1}$. Its definition
is also found in \eqref{eq:eigenmeasure}.

>>>>

Kesten \cite{kesten:1973} showed that, when $A_t$ are almost
surely non-negative, has no row or column of only zeros, and
$B_t$ is almost surely non-negative and is not equal to the null
vector with probability 1, then the strictly stationary solution to
the equation $V \overset{d}{=} A V + B$ has power-law tails
for its marginal distributions, assuming the following conditions (M)
and (A):
\begin{itemize}
\item Condition (M)
  \begin{enumerate}
  \item The top Lyapunov exponent
    \[
    \gamma = \inf_{n \geq 1} {1 \over n}\E \log \|A_n \cdots A_1\|
    \]
    is negative.
  \item There exists $\xi > 0$ such that
    \[
    1 = \lambda(\xi) = \lim_{n \to \infty} {1 \over n} \log \E \|A_n \cdots A_1\|^\xi
    \]
  \item $\E (\|A_1\|^\xi \log^+\|A_1\|) < \infty$
  \item $\E |B_1|^\xi < \infty$
  \end{enumerate}
\item Condition (A) : The group generated by
  \[
  \{\log\rho(s): s = A_n \cdots A_1 \text{ for some } n \geq 1\}
  \]
  is dense in $\reals$, where $\rho(s)$ denotes the spectral
  radius of matrix $s$.
\end{itemize}
Upon these conditions, Kesten's theorem gives
\begin{equation*}
  u^\xi \P(u^{-1} V \in \cdot) \overset{v}{\to} \mu_\xi(\cdot)
\end{equation*}
where $\mu_\xi$ is a non-null Radon measure on
$\reals^d_+ \setminus \{0\}$ with the property
$\mu_\xi(a A) = a^{-\xi} \mu_\xi(A)$.

Recently, Collamore and Mentemeier \cite{collamore:mentemeier:2016}
extended Kesten's result and gave an explicit expression for $\mu_\xi$:
\begin{equation}
  \label{eq:CollamoreMentemeierIntro}
  \lim_{u \to \infty} u^{\xi} \E \left[
    f(u^{-1} V)
    \right]
  =
  {C \over \lambda'(\xi)}  
  \int_{\sphere^{d-1}_+ \times R} e^{-\xi s} f(e^s x) \ell_\xi(dx) ds
\end{equation}
where $C$ is a constant (cf. (2.15) of Collamore and Mentemeier
\cite{collamore:mentemeier:2016}), $f(\cdot)$ is any bounded
continuous function on $\reals^{d}_+ \setminus \{0\}$  and
$\ell_\xi$ is a probability measure on $\sphere_+^{d-1}$. Its definition
is also found in \eqref{eq:eigenmeasure}.
